---
title: "ADC Training Footage Inter-Coder Reliability"
author: "Sophie Berdugo"
date: "23/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Development Variables

### Video UID: a9f7d6e1-f513-4c49-beaa-65656d7486ff
### Video Data and Time: 2003-12-15 | 17:19:13

**Rater 1: Sophie Berdugo**
**Rater 2: Alejandro Diaz-Cavieres**

Load libraries for analysis
```{r message=FALSE, warning=FALSE}
library(tidyverse) #Load tidyverse to use the tidyverse package
library(irr) #Load the irr package to retrieve packages relating to inter-rater reliability.
```

# Variables
This analysis involves establishing the levels of inter-rater reliability for various variables relating to  nut-cracking development and model selection. These variables are:

* Bout duration
* Bout outcome
* Strikes per nut
* Peering duration
* Behavioural episode class
* Behavioural episode object(s)
* Behavioural episode fundamental action(s)

The inter-rater reliability analysis utilised depends on the level of measurement of each variable under investigation. The levels of measurement and corresponding test of inter rater reliability for each variable can be found in Table 1, below:

*Table 1*

| Variable                                  | Level of Measurement | Approach                           |
| :---------------------------------------- | :------------------- | :--------------------------------- |
| Bout duration                             | Ratio                | Intraclass correlation coefficient |
| Bout outcome                              | Nominal              | Cohen's kappa                      |
| Strikes per nut                           | Ratio                | Intraclass correlation coefficient |
| Peering duration                          | Ratio                | Intraclass correlation coefficient |
| Behavioural episode class                 | Nominal              | Cohen's kappa                      |
| Behavioural episode object(s)             | Nominal              | Cohen's kappa                      |
| Behavioural episode fundamental action(s) | Nominal              | Cohen's kappa                      |

## Bout Duration

Import data frames from csv files.
```{r}
sb_adc_bout_duration <- read_csv("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Bout duration.csv")
sb_adc_bout_duration
```
Calculate ICC for two coders
```{r}
icc(sb_adc_bout_duration, #data frame
    model = "twoway", #two-way model selected as the selected raters are the only raters of interest (Koo & Li, 2016)
    type = "consistency", #consistency between the raters to be calculated
    unit = "single", #measurement from a single rater as the basis of the actual measurement
    r0 = 0, #specification of the null hypothesis
    conf.level = 0.95) #confidence level
```
**ICC estimates and their 95% confidence intervals were calculated using R (v. 4.0.3) based on a single rater (k = 2), consistency, two-way mixed effects model. The ICC score indicated excellent reliability.** 

## Number of strikes

Import data frame from csv file
```{r}
sb_adc_strikes <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Number of strikes.csv"))
sb_adc_strikes
```
Calculate ICC for two coders
```{r}
icc(sb_adc_strikes, #data frame
    model = "twoway", #two-way model selected as the selected raters are the only raters of interest (Koo & Li, 2016)
    type = "agreement", #absolute agreement between the raters to be calculated
    unit = "single", #measurement from a single rater as the basis of the actual measurement
    r0 = 0, #specification of the null hypothesis
    conf.level = 0.95) #confidence level
```
**ICC estimates and their 95% confidence intervals were calculated using R (v. 4.0.3) based on a single rater (k = 2), agreement, two-way mixed effects model. The ICC score indicated perfect reliability.**

## Bout Outcome

Import data from csv file

```{r}
sb_adc_bout_outcome <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Bout outcome.csv"))
sb_adc_bout_outcome
```

```{r}
kappa2(sb_adc_bout_outcome[,c(1,2)], "unweighted")
```

## Behavioural episode duration

Import data from csv file

```{r}
sb_adc_behavioural_episode_duration <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Behavioural episode duration.csv"))
sb_adc_behavioural_episode_duration
```

Calculate ICC for two coders
```{r}
icc(sb_adc_behavioural_episode_duration, #data frame
    model = "twoway", #two-way model selected as the selected raters are the only raters of interest (Koo & Li, 2016)
    type = "consistency", #consistency between the raters to be calculated
    unit = "single", #measurement from a single rater as the basis of the actual measurement
    r0 = 0, #specification of the null hypothesis
    conf.level = 0.95) #confidence level
```

## Behavioural Episode Class

Import data from csv file

```{r}
sb_adc_behavioural_episode_class <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Behavioural Episode Class.csv"))
sb_adc_behavioural_episode_class
```

Calculate Cohen's kappa
```{r}
kappa2(sb_adc_behavioural_episode_class[,c(1,2)], "unweighted")
```

### Behavioural Episode Object(s)

```{r}
sb_adc_behavioural_episode_objects <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Behavioural episode objects.csv"))
sb_adc_behavioural_episode_objects
```

Calculate Cohen's kappa
```{r}
kappa2(sb_adc_behavioural_episode_objects[,c(1,2)], "unweighted")
```

### Behavioural Episode Action(s)

```{r}
sb_adc_behavioural_episode_actions <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Behavioural episode actions.csv"))
sb_adc_behavioural_episode_actions
```

Calculate Cohen's kappa
```{r}
kappa2(sb_adc_behavioural_episode_actions[,c(1,2)], "unweighted")
```

## Peering Duration

Import data frames from csv files.
```{r}
sb_adc_peering_duration <- read_csv("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Peering duration.csv")
sb_adc_peering_duration
```

Calculate ICC for two coders
```{r}
icc(sb_adc_peering_duration, #data frame
    model = "twoway", #two-way model selected as the selected raters are the only raters of interest (Koo & Li, 2016)
    type = "consistency", #consistency between the raters to be calculated
    unit = "single", #measurement from a single rater as the basis of the actual measurement
    r0 = 0, #specification of the null hypothesis
    conf.level = 0.95) #confidence level
```

# Retraining

## Peering Duration

Import data frames from csv files.
```{r}
retrained_sb_adc_peering_duration <- read_csv("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Retrained/Peering duration.csv")
retrained_sb_adc_peering_duration
```

Calculate ICC for two coders
```{r}
icc(retrained_sb_adc_peering_duration, #data frame
    model = "twoway", #two-way model selected as the selected raters are the only raters of interest (Koo & Li, 2016)
    type = "consistency", #consistency between the raters to be calculated
    unit = "single", #measurement from a single rater as the basis of the actual measurement
    r0 = 0, #specification of the null hypothesis
    conf.level = 0.95) #confidence level
```

# Behavioural Episode Duration

Import data frames from csv files.
```{r}
retrained_sb_adc_behavioural_episode_duration <- read_csv("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Retrained/Behavioural episode duration.csv")
retrained_sb_adc_behavioural_episode_duration
```

Calculate ICC for two coders
```{r}
icc(retrained_sb_adc_behavioural_episode_duration, #data frame
    model = "twoway", #two-way model selected as the selected raters are the only raters of interest (Koo & Li, 2016)
    type = "consistency", #consistency between the raters to be calculated
    unit = "single", #measurement from a single rater as the basis of the actual measurement
    r0 = 0, #specification of the null hypothesis
    conf.level = 0.95) #confidence level
```

## Behavioural Episode Class

```{r}
retrained_sb_adc_behavioural_episode_class <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Retrained/Behavioural episode class.csv"))
retrained_sb_adc_behavioural_episode_class
```

Calculate Cohen's kappa
```{r}
kappa2(retrained_sb_adc_behavioural_episode_class[,c(1,2)], "unweighted")
```

## Behavioural Episode Objects

```{r}
retrained_sb_adc_behavioural_episode_objects <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Retrained/Behavioural episode objects.csv"))
retrained_sb_adc_behavioural_episode_objects
```

Calculate Cohen's kappa
```{r}
kappa2(retrained_sb_adc_behavioural_episode_objects[,c(1,2)], "unweighted")
```

## Behavioural Episode Actions

```{r}
retrained_sb_adc_behavioural_episode_actions <- read_csv(("~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Alejandro Diaz-Cavieres/Training/Clean Data/Retrained/Behavioural episode actions.csv"))
retrained_sb_adc_behavioural_episode_actions
```

Calculate Cohen's kappa
```{r}
kappa2(retrained_sb_adc_behavioural_episode_actions[,c(1,2)], "unweighted")
```
