---
title: "Cleaning VM Training Data"
author: "Sophie Berdugo"
date: "04/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Video UID: 8cd3b20b-f527-4092-907c-0311c8f3cfa6
### Video Data and Time: 2010-01-03 | 08:05:33

**Import Data**
Load tidyverse library to use the tidyverse package.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

**Import CSV file**
Import csv file of training data from location on machine. Data frame assigned to a variable called 'training'.

``` {r message=FALSE, warning=FALSE}
training <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_data_updated.csv')
training
```
**Change Column Names**

``` {r message=FALSE, warning=FALSE}
names <- c("ObservationID", "ObservationDate", "Description", "MediaFile", "TotalLength", "FPS", "Subject", "Behaviour", "BehaviouralCategory", "Modifiers", "BehaviourType", "Start", "Stop", "Duration", "CommentStart", "CommentStop") #Create the vector of names
training <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_data_updated.csv', col_names = names) #Add the vector 'names' to the tibble and reimport the csv file with the col_names changed
training <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_data_updated.csv', col_names = names, skip = 1) #Remove the original column names by using the skip function
glimpse(training)
```

**Remove columns**
Use dplyr to remove multiple columns which are not included in the analysis.

``` {r message=FALSE, warning=FALSE}
select(training, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
training <- select(training, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
glimpse(training)
```

**Separate out the ObservationDate column**

```{r, message=FALSE, warning=FALSE}
separate(training, ObservationDate, c('ObservationDate', 'ObservationTime'), 11) #separate the ObservationDate column into two new columns, separating the data at position 11
glimpse(training)
```

**Separate out the Modifiers column**

Subset the Modifier Column

```{r}
filter(training, Behaviour == 'End Bout') #extract the rows that meet the logical criteria of being exactly equal to 'End Bout'
end_bout <- filter(training, Behaviour == 'End Bout') #create a new variable for this subset of End Bout data
separate(end_bout, Modifiers, c('CompleteBout', 'Strikes', 'Outcome', 'Learner', 'MaternalModel', 'LearnerName', 'ModelTolerance', 'ModelIntolerance')) #separate the Modifiers column in this end_bout data into new columns, separating the data at the place that R finds a non-alpha numerica character
end_bout #print 
```

**Create a new column to number the bouts**

```{r}
j = 0 #create a new counting variable
training$bout.nr = 0 #create a new empty column
for(i in 1:nrow(training)){ #loop over all rows
  if(training$Behaviour[i] == 'Start Bout'){ #if the row says 'Start Bout', the bout counter is updated by 1
    j = j+1
  }
  training$bout.nr[i] = j #give the row the bout number
}
```
