#Data Cleaning for Practice Inter-Coder Reliability Video Coding
##Sophie Berdugo and Zhangzhuoran Dai 
###Video UID: 357b79c7-9ce6-42a8-81f1-2a732dc483c5
###Video Data: 2012-02-06

**Import Data**
Load tidyverse library to use the tidyverse package.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

Import csv file of practice video coding data from location on machine. Data frame assigned to a variable called 'practice'.

``` {r}
practice <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/R Projects/Zhangzhuoran Dai/Training Data/practice footage.csv')
glimpse(practice)
```

**Change Column Names**

Change the column names in the tibble. 
1. Create the vector of names 
2. Add the vector 'names' to the tibble and reimport the csv file with the col_names changed
3. Remove the original column names by using the skip function

``` {r message=FALSE, warning=FALSE}
names <- c("ObservationID", "ObservationDate", "Description", "MediaFile", "TotalLength", "FPS", "Subject", "Behaviour", "BehaviouralCategory", "Modifiers", "BehaviourType", "Start", "Stop", "Duration", "CommentStart", "CommentStop")
practice <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/R Projects/Zhangzhuoran Dai/Training Data/practice footage.csv', col_names = names)
practice <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/R Projects/Zhangzhuoran Dai/Training Data/practice footage.csv', col_names = names, skip = 1)
glimpse(practice)
```

