---
title: "VM Training Bouts by Subject"
author: "Sophie Berdugo"
date: "05/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Video UID: 8cd3b20b-f527-4092-907c-0311c8f3cfa6
### Video Data and Time: 2010-01-03 | 08:05:33

#### VM Tua

**Import Data**
Load tidyverse library to use the tidyverse package.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

**Import CSV file**
Import csv file of training data from location on machine. Data frame assigned to a variable called 'vm_tua'.

``` {r message=FALSE, warning=FALSE}
vm_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_tua.csv')
vm_tua
```

**Change Column Names**

``` {r message=FALSE, warning=FALSE}
names <- c("ObservationID", "ObservationDate", "Description", "MediaFile", "TotalLength", "FPS", "Subject", "Behaviour", "BehaviouralCategory", "Modifiers", "BehaviourType", "Start", "Stop", "Duration", "CommentStart", "CommentStop") #Create the vector of names
vm_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_tua.csv', col_names = names) #Add the vector 'names' to the tibble and reimport the csv file with the col_names changed
vm_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_tua.csv', col_names = names, skip = 1) #Remove the original column names by using the skip function
glimpse(vm_tua)
```

**Remove columns**
Use dplyr to remove multiple columns which are not included in the analysis.

``` {r message=FALSE, warning=FALSE}
select(vm_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
vm_tua <- select(vm_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
glimpse(vm_tua)
```

**Create a new column to number the bouts**

```{r}
j = 0 #create a new counting variable
vm_tua$bout.nr = 0 #create a new empty column
for(i in 1:nrow(vm_tua)){ #loop over all rows
  if(vm_tua$Behaviour[i] == 'Start Bout'){ #if the row says 'Start Bout', the bout counter is updated by 1
    j = j+1
  }
  vm_tua$bout.nr[i] = j #give the row the bout number
}
```

**Get the Modifier information for each bout**

```{r}
bout.info = lapply(unique(vm_tua$bout.nr), function(x){
  print(x)
  set.data = subset(vm_tua, bout.nr == x) #select only the bout in question
  bout.info = unlist(
    strsplit(
      set.data$Modifiers[set.data$Behaviour == 'End Bout'],
      split = '|',
      fixed = T)) #This takes apart the information in the End Bout Modifier
  x.bout = data.frame(
    bout.nr = x,
    CompleteBout = bout.info[1], #Assign a name to each Modifier into a new column
    Strikes = bout.info[2],
    Outcome = bout.info[3],
    Learner = bout.info[4],
    MaternalModel = bout.info[5],
    LearnerName = bout.info[6],
    ModelTolerance = bout.info[7],
    ModelIntolerance = bout.info[8]
  )
  return(x.bout) #Puts out that data frame
})
bout.info = do.call(rbind, bout.info) #Turns the list for all the bouts into a data frame again
```

#### SB Tua

**Import CSV file**
Import csv file of training data from location on machine. Data frame assigned to a variable called 'sb_tua'.

``` {r message=FALSE, warning=FALSE}
sb_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/SB_training_tua.csv')
sb_tua
```

**Change Column Names**

``` {r message=FALSE, warning=FALSE}
sb_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/SB_training_tua.csv', col_names = names) #Add the vector 'names' to the tibble and reimport the csv file with the col_names changed
sb_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/SB_training_tua.csv', col_names = names, skip = 1) #Remove the original column names by using the skip function
glimpse(sb_tua)
```

**Remove columns**
Use dplyr to remove multiple columns which are not included in the analysis.

``` {r message=FALSE, warning=FALSE}
select(sb_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
sb_tua <- select(sb_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
glimpse(sb_tua)
```

**Create a new column to number the bouts**

```{r}
k = 0 #create a new counting variable
sb_tua$bout.nr = 0 #create a new empty column
for(i in 1:nrow(sb_tua)){ #loop over all rows
  if(sb_tua$Behaviour[i] == 'Start Bout'){ #if the row says 'Start Bout', the bout counter is updated by 1
    k = k+1
  }
  sb_tua$bout.nr[i] = k #give the row the bout number
}
```

**Get the Modifier information for each bout**

```{r}
sb_tua_bout_info = lapply(unique(sb_tua$bout.nr), function(y){
  print(y)
  set.data = subset(sb_tua, bout.nr == y) #select only the bout in question
  sb_tua_bout_info = unlist(
    strsplit(
      set.data$Modifiers[set.data$Behaviour == 'End Bout'],
      split = '|',
      fixed = T)) #This takes apart the information in the End Bout Modifier
  y.bout = data.frame(
    bout.nr = y,
    CompleteBout = bout.info[1], #Assign a name to each Modifier into a new column
    Strikes = bout.info[2],
    Outcome = bout.info[3],
    Learner = bout.info[4],
    MaternalModel = bout.info[5],
    LearnerName = bout.info[6],
    ModelTolerance = bout.info[7],
    ModelIntolerance = bout.info[8]
  )
  return(y.bout) #Puts out that data frame
})
sb_tua_bout_info = do.call(rbind, sb_tua_bout_info) #Turns the list for all the bouts into a data frame again
```

Subset sb_tua_bout_info to just the first 27 rows

```{r}
slice(sb_tua_bout_info, 1:27) #select rows by position
sb_tua_info <- slice(sb_tua_bout_info, 1:27) #create new data frame of subset
sb_tua_info <- select(sb_tua_info, -c(bout.nr)) #remove bout.nr column
sb_tua_info
```

Rename VM bout.info data frame

```{r}
vm_tua_info <- bout.info
```

