---
title: "VM Training Bouts by Subject"
author: "Sophie Berdugo"
date: "05/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Video UID: 8cd3b20b-f527-4092-907c-0311c8f3cfa6
### Video Data and Time: 2010-01-03 | 08:05:33

#### VM Tua

Load libraries for analysis

```{r message=FALSE, warning=FALSE}
library(tidyverse) #Load tidyverse to use the tidyverse package
library(irr) #Load the irr package to retrieve packages relating to inter-rater reliability.
```

**Import CSV file**
Import csv file of training data from location on machine. Data frame assigned to a variable called 'vm_tua'.

``` {r message=FALSE, warning=FALSE}
vm_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_tua.csv')
vm_tua
```

**Change Column Names**

``` {r message=FALSE, warning=FALSE}
names <- c("ObservationID", "ObservationDate", "Description", "MediaFile", "TotalLength", "FPS", "Subject", "Behaviour", "BehaviouralCategory", "Modifiers", "BehaviourType", "Start", "Stop", "Duration", "CommentStart", "CommentStop") #Create the vector of names
vm_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_tua.csv', col_names = names) #Add the vector 'names' to the tibble and reimport the csv file with the col_names changed
vm_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/VM_training_tua.csv', col_names = names, skip = 1) #Remove the original column names by using the skip function
glimpse(vm_tua)
```

**Remove columns**
Use dplyr to remove multiple columns which are not included in the analysis.

``` {r message=FALSE, warning=FALSE}
select(vm_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
vm_tua <- select(vm_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
glimpse(vm_tua)
```

**Create a new column to number the bouts**

```{r}
j = 0 #create a new counting variable
vm_tua$bout.nr = 0 #create a new empty column
for(i in 1:nrow(vm_tua)){ #loop over all rows
  if(vm_tua$Behaviour[i] == 'Start Bout'){ #if the row says 'Start Bout', the bout counter is updated by 1
    j = j+1
  }
  vm_tua$bout.nr[i] = j #give the row the bout number
}
```

**Get the Modifier information for each bout**

```{r}
bout.info = lapply(unique(vm_tua$bout.nr), function(x){
  print(x)
  set.data = subset(vm_tua, bout.nr == x) #select only the bout in question
  bout.info = unlist(
    strsplit(
      set.data$Modifiers[set.data$Behaviour == 'End Bout'],
      split = '|',
      fixed = T)) #This takes apart the information in the End Bout Modifier
  x.bout = data.frame(
    bout.nr = x,
    CompleteBout = bout.info[1], #Assign a name to each Modifier into a new column
    Strikes = bout.info[2],
    Outcome = bout.info[3],
    Learner = bout.info[4],
    MaternalModel = bout.info[5],
    LearnerName = bout.info[6],
    ModelTolerance = bout.info[7],
    ModelIntolerance = bout.info[8]
  )
  return(x.bout) #Puts out that data frame
})
bout.info = do.call(rbind, bout.info) #Turns the list for all the bouts into a data frame again
```

#### SB Tua

**Import CSV file**
Import csv file of training data from location on machine. Data frame assigned to a variable called 'sb_tua'.

``` {r message=FALSE, warning=FALSE}
sb_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/SB_training_tua.csv')
sb_tua
```

**Change Column Names**

``` {r message=FALSE, warning=FALSE}
sb_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/SB_training_tua.csv', col_names = names) #Add the vector 'names' to the tibble and reimport the csv file with the col_names changed
sb_tua <- read_csv('~/Documents/Oxford/DPhil/Project Components/Inter-Coder Reliability/Data/Victoire Martignac/Training Data/SB_training_tua.csv', col_names = names, skip = 1) #Remove the original column names by using the skip function
glimpse(sb_tua)
```

**Remove columns**
Use dplyr to remove multiple columns which are not included in the analysis.

``` {r message=FALSE, warning=FALSE}
select(sb_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
sb_tua <- select(sb_tua, -c(Description, MediaFile, TotalLength, FPS, BehaviouralCategory, BehaviourType, CommentStart, CommentStop))
glimpse(sb_tua)
```

**Create a new column to number the bouts**

```{r}
k = 0 #create a new counting variable
sb_tua$bout.nr = 0 #create a new empty column
for(i in 1:nrow(sb_tua)){ #loop over all rows
  if(sb_tua$Behaviour[i] == 'Start Bout'){ #if the row says 'Start Bout', the bout counter is updated by 1
    k = k+1
  }
  sb_tua$bout.nr[i] = k #give the row the bout number
}
```

**Get the Modifier information for each bout**

```{r}
sb_tua_bout_info = lapply(unique(sb_tua$bout.nr), function(y){
  print(y)
  set.data = subset(sb_tua, bout.nr == y) #select only the bout in question
  sb_tua_bout_info = unlist(
    strsplit(
      set.data$Modifiers[set.data$Behaviour == 'End Bout'],
      split = '|',
      fixed = T)) #This takes apart the information in the End Bout Modifier
  y.bout = data.frame(
    bout.nr = y,
    CompleteBout = bout.info[1], #Assign a name to each Modifier into a new column
    Strikes = bout.info[2],
    Outcome = bout.info[3],
    Learner = bout.info[4],
    MaternalModel = bout.info[5],
    LearnerName = bout.info[6],
    ModelTolerance = bout.info[7],
    ModelIntolerance = bout.info[8]
  )
  return(y.bout) #Puts out that data frame
})
sb_tua_bout_info = do.call(rbind, sb_tua_bout_info) #Turns the list for all the bouts into a data frame again
```

Subset sb_tua_bout_info to just the first 27 rows

```{r}
slice(sb_tua_bout_info, 1:27) #select rows by position
sb_tua_info <- slice(sb_tua_bout_info, 1:27) #create new data frame of subset
sb_tua_info <- select(sb_tua_info, -c(bout.nr)) #remove bout.nr column
sb_tua_info
```

Rename VM bout.info data frame

```{r}
vm_tua_info <- bout.info
```

#### Bout Outcome Inter-Coder Reliabiliy

The three potential bout outcomes are:

1. *Successful* - The nut is cracked open using the hammer and anvil composite and the full kernel is retrieved and eaten by an individual (not necessarily by focal subject, if kernel is scrounged). 
2. *Smash* - The nut is cracked open using hammer and anvil, but the kernel is smashed into multiple pieces and each piece is eaten separately.
3. *Failed* - A different nut is placed on the anvil following displacement of the original nut; or, the nut is not retrieved or not eaten by any individual. 

This data is nominal so an unweighted Cohen's kappa will be used to establish the concordance between two independent observers. 
rater1 = SB, rater2 = ZD

**Combine the bout outcome columns for Tua data**
```{r}
sb_tua_outcome <- select(sb_tua_info, Outcome) #select the column for bout outcome from sb data frame
vm_tua_outcome <- select(vm_tua_info, Outcome) #select the column for bout outcome from vm data frame
tua_outcome <- bind_cols(sb_tua_outcome, vm_tua_outcome) #combine two columns to get tua bout outcome SB and VM side-by-side
tua_outcome <- tua_outcome %>%
  rename(
    SB = Outcome...1,
    VM = Outcome...2
  ) #rename the two columns and override original data frame of tua_outcome to include renamed columns
tua_outcome #print
```

Calculate Cohen's kappa for two coders.
?kappa2
```{r}
kappa2(tua_outcome[,c(1,2)], "unweighted")
```

### Number of strikes

The variable *Strikes* records the number of strikes performed by the focal individual on a nut in the whole nut-cracking bout. This is an exact number that is manually inputted by the coder. 

This data is ratio, and so intraclass correlations (ICC) will be used to establish the reliability between two independent coders. In accordance with Koo & Li's (2016) guidelines on ICC model selection, the method used here will be a two-way, mixed-effects, single rater absolute agreement ICC.

**Combine the strikes columns for Tua data**
```{r}
sb_tua_strikes <- select(sb_tua_info, Strikes) #select the column for strikes from SB data frame
vm_tua_strikes <- select(vm_tua_info, Strikes) #select the column for strikes from SB data frame
tua_strikes <- bind_cols(sb_tua_strikes, vm_tua_strikes) #combine two columns to get tua strikes SB and VM side-by-side
tua_strikes <- tua_strikes %>%
  rename(
    SB = Strikes...1,
    VM = Strikes...2
  ) #rename the two columns and override original data frame of tua_outcome to include renamed columns
tua_strikes #print
```

Calculate ICC for two coders
```{r}
icc(tua_strikes, #data frame
    model = "twoway", #two-way model selected as the selected raters are the only raters of interest (Koo & Li, 2016)
    type = "agreement", #absolute agreement between the raters to be calculated
    unit = "single", #measurement from a single rater as the basis of the actual measurement
    r0 = 0, #specification of the null hypothesis
    conf.level = 0.95) #confidence level
```

